What is disputed on the web?

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
Added text to accompany cluster data

Dispute Finder is one such agent that we are developing to provide real-time dispute recognition to users by identifying disputed claims that appear in web pages. Future iterations of Dispute Finder and other such agents will be designed to work with other media such as television or radio, as well as augmented reality applications. We envision a device that provides real-time feedback to users regarding claims made in a conversation or presentation. Such a device would augment individuals' intuitive recognition of that a disputed claim is being made.

@@

\x{Named entity recognition}

\x{Look at what noun phrases were most disputed at particular years.}
\x{Look at what noun phrases were most disputed on particular days.}

\x{We remove exact-match strings from the same domain - to avoid republishing of same article.}

>>>>

Dispute Finder~\cite{Ennals2010} is one such agent that we are developing to provide real-time dispute recognition to users by identifying disputed claims that appear in web pages. Future iterations of Dispute Finder and other such agents will be designed to work with other media such as television or radio, as well as augmented reality applications. We envision a device that provides real-time feedback to users regarding claims made in a conversation or presentation. Such a device would augment individuals' intuitive recognition of that a disputed claim is being made.

@@

Figure~\ref{cluster-figure} shows the most frequently occurring word clusters that we found for each noun. Most of these will make sense to people who have been following news in the united states. For example, we see that disputed claims about Obama often talk about his nobel prize or his birth certificate, and that President Ahmadinejad of Iran did not actually say that Israel should be wiped off the map (which the authors had not previously realized). Some of the word clusters are not particularly interesting - for example many claims talk about the united states, even when that is not an important part of what is disputed.
